---
title: "Growth and yield model (evenaged stands)"
author: Roberto Scotti
date: November, 2017
output:
  html_document:
    smart: false
  html_notebook: default
---


# Introduction

![General flowchart](figure/FGaYmod.svg){ width=80% }

# Workplan: main modules
~~~~~~~
access inventory data  
initialiazie stands list  
  
choose appropriate:  
	* Site Index classification tool  
	* height by dbh estimation model  
	* dbh growth function  
  
CHECK  
	all required info available?  
		YES, proceed to GROW  
	Age missing?  
		YES, goto (A)  
	Site Index missing?  
		NO, goto (A)  
		compute dominant height  
		assess Site Index  
		update stands list  
		(back to (0))  
	(A) other problems (under dev.), STOP  

GROW  
	(1) compile stand table  
	estimate dominant height and mean height for all dbh classes  
	[evaluate if thinning is required and execute treatment]   
	estimate dbh growth for each class  
	update stand table  
	ending condition attained?  
		NO, (back to (1))  
final stand table - produce summary 
~~~~~~~

# Implementation

## access inventory data

```{r }
library(googlesheets)
library(dplyr)
library(tidyr)
library(magrittr)
getwd()
source("Functions/access2DB.R", echo=F, verbose=F)
# t <- 
tibble::tribble(
  ~table,              ~sheet,
  "species",           "Specie",
  "stands",            "AdS",
  "dbh_tally",         "Cavallettamento",
  "heights",           "Altezze",
  "increment_borings", "Carotine") %>% 
  group_by(sheet) %>% 
  do(assign(.$table, gs_read(DataBase, ws=.$sheet), pos=1)) %>%
  rm()
# save(list=as.vector(t$table), file="GO_DonatoDB.Rdata")
# load("../GO_DonatoDB.Rdata")
dbh_tally <- dbh_tally %>% 
  gather("species", "freq", -id_ads, -d_130, na.rm=T) %>%
  left_join(select(stands, id_ads, sup_m_quadri)) %>%
  mutate(n_ha = 10000 * freq / sup_m_quadri) 

```

```{r}
# dominant diameter
cum_frq <- 
  dbh_tally %>%
  group_by(id_ads, d_130) %>%
  summarise(n_ha_tot = sum(n_ha)) %>%
  group_by(id_ads) %>%
  arrange(desc(d_130)) %>%
  do(mutate(., cum_n_ha = cumsum(n_ha_tot)))
d_dom <-
  cum_frq %>%
  filter(cum_n_ha >= 100) %>%
  group_by(id_ads) %>%
  filter(d_130 == max(d_130)) %>%
  mutate(n_ha_tot = n_ha_tot - (cum_n_ha - 100)) %>%
  union(filter(cum_frq, cum_n_ha < 100)) %>%
  summarise(n_tot = sum(n_ha_tot), 
            d_dom = sqrt(sum(n_ha_tot * d_130^2)/n_tot ))

source("Functions/F_SiteIndex_MN94.R")
current_year <- 2017
# dominant height and 
# site class  evaluation
h_dom <-
  heights %>%
  filter(sp == "dou") %>%
  group_by(id_ads) %>%
  do(hm=loess(h~diam, .)) %>%
  left_join(d_dom) %>%
  group_by(id_ads) %>%
  do(d_dom = .$d_dom, 
     f = predict(.$hm[[1]], data.frame(diam=.$d_dom), se = TRUE)) %>%
  group_by(id_ads) %>%
  do(d_dom = .$d_dom[[1]], 
     h_dom = (.$f[[1]]$fit[[1]]),
     se.h_dom = (.$f[[1]]$se.fit[[1]])
     ) %>%
  left_join(select(stands, id_ads, eta2017)) %>%
  mutate(current_year = 2017, age = eta2017, d_dom = d_dom[[1]],
         h_dom = h_dom[[1]],  se.h_dom = se.h_dom[[1]],
         plantation_year = 2017 - eta2017,
         SI_MN94_50 = dougSI_MN94(age, h_dom)) %>%
  select(-eta2017)

```


[[to be continued ...]]
